\documentclass[a4paper,10pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{enumitem}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\usepackage{amsmath}

\usepackage{titlesec}

% تنظیمات برای حذف تورفتگی‌ها و زیبایی تیترها
\titleformat{\section}{\large\bfseries\uppercase}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{12pt}{8pt}
\newcommand{\cvsubsection}[1]{\noindent{\textsc{#1}}}
\begin{document}

% هدر متمرکز و شکیل
\begin{center}
{\LARGE \textbf{Pardis Derakhshandeh}} \\
Linguistics Department, Stony Brook University \\
100 Nicolls Road, Stony Brook, NY 11790 \\
Email: \href{mailto:pardis.derakhshandeh@stonybrook.edu}{pardis.derakhshandeh@stonybrook.edu} \\
Website: \href{https://pardisderakhshandeh.github.io}{pardisdrk.github.io}
\end{center}

\section*{Research Interests}
\begin{tabular}{@{}l p{0.8\linewidth}@{}}
\textbf{Theoretical}  & Formal Syntax · Morphosyntax · Argument Structure · Ergativity and Complex Alignment \\
\textbf{Languages}  & \textbf{Western Iranian languages:} Behbahani, Kurdish Varieties (Kurmanji, Sorani, Hawrami), Persian, and Southwestern Varieties  (Dashti, Davani) \\
                   & \textbf{Historical:} Old and Middle Persian: diachronic development of ergative alignment \\
\end{tabular}

\section*{Education}
\textbf{Ph.D. in Linguistics} \hfill 2021--Present \\
Stony Brook University, Stony Brook, NY \\
Dissertation: \textit{The Architecture of Argument Licensing in Behbahani} \\
Committee: Francisco Ordóñez (Chair), Richard Larson, Faruk Akku\c{s} (UMass Amherst)\\

\vspace{4pt}

\textbf{M.A. in Linguistics} \hfill 2018 \\
University of Kurdistan, Sanandaj, Iran\\

\vspace{4pt}

\textbf{B.A. in English Language and Literature} \hfill 2015 \\
University of Kurdistan, Sanandaj, Iran\\

\vspace{4pt}

\noindent \textsc{Non-Degree Seeking}\\
\textbf{Summer Program in Linguistics and Cognitive Science} \hfill 2020 \\
NYI Global Institute of Cultural, Cognitive, and Linguistic Studies

\section*{Publications and Conference Abstracts}
\subsection*{Manuscripts in Preparation}
\begin{itemize}[leftmargin=0.5cm]
  \item \textbf{Derakhshandeh, P.} \textit{Split Alignment beyond Case in Behbahani}. 
    Manuscript in preparation. (Draft available upon request).

    \item \textbf{Derakhshandeh, P.} \textit{The Syntax–Morphology Interface in Behbahani: A Case Study of Stem Alternation}. 
    Manuscript in preparation.(Draft available upon request).

\end{itemize}
\subsection*{Peer-reviewed Conference Abstracts}
\begin{itemize}[leftmargin=0.5cm, itemsep=0.3em]
    \item \textbf{Derakhshandeh, P.} (2026). Beyond Tense: The Structural Autonomy of StemP in Behbahani. \textit{The 50th Annual Penn Linguistics Conference (PLC 50) Handbook}.
    
    \item \textbf{Derakhshandeh, P.} (2025). Introducing Behbahani. \textit{2025 LSA Annual Meeting Program}.
\end{itemize}

\section*{\textbf{Presentations and Talks}}
\begin{itemize}[leftmargin=0.5cm]

\item \textbf{2026.} \textit{Beyond Tense: The Structural Autonomy of StemP in Behbahani}. 
Poster presented at the 50th Annual Penn Linguistics Conference (PLC 50), 
University of Pennsylvania, Philadelphia, PA.

\item \textbf{2025.} \textit{Introducing Behbahani}. 
Annual Meeting of the Linguistic Society of America, Philadelphia, PA.

\item \textbf{2024.} \textit{Split Alignment beyond Case}. 
Stony Brook University, Stony Brook, NY.

\item \textbf{2023.} \textit{Alignment in Behbahani}. 
Stony Brook University, Stony Brook, NY.

\item \textbf{2018.} \textit{Locus of the NegP in Behbahani}. 
University of Kurdistan, Sanandaj, Iran.

\item \textbf{2017.} Speaker, “What is Linguistics?” Workshop for undergraduate students. 
University of Kurdistan, Sanandaj, Iran.

\item \textbf{2016.} \textit{A Study of Color Metaphors in Behbahani}. 
University of Kurdistan, Sanandaj, Iran.

\end{itemize}
\section*{Research Project}
\begin{itemize}
\item \textbf{Lead Organizer, ``Introducing Behbahani to the Linguistics Community''} \hfill May–December 2024

\begin{itemize}[leftmargin=0.5cm]
\item Organized an LSA Annual Meeting session dedicated to linguistic research on Behbahani, a less-studied Iranian language.
\item Coordinated a team of colleagues and ten student presenters contributing analyses of Behbahani.
\item Mentored student researchers by providing linguistic data and refining research questions.
\item Guided the organization and analysis of linguistic data for conference presentations.
\item Provided detailed feedback on research design and presentation materials.
\end{itemize}

\end{itemize}

\section*{Organized Sessions and Events}

\begin{itemize}

\item \textbf{LSA Organized Session:} 
``Linguists, Meet Behbahani: A Syntax, Morphology, Phonology, and Phonetics Data Blitz.'' 
Linguistic Society of America Annual Meeting (with Robert Hoberman and Daniel Greeson). 
January 2025.

\item \textbf{Scholarly Seminar on Alice Munro} (Lead Organizer).  
Department of English Linguistics and Literature, University of Kurdistan.  
Sanandaj, Iran. November 2013.

\end{itemize}

\section*{Teaching Experience}
\subsection*{Stony Brook University - Primary Instructor}
\begin{itemize}
   \item LIN 200: Language in the United States \hfill Winter 2026, 2024, 2023
    \item LIN 541: Sociolinguistics \hfill Summer 2025
    \item LIN 541: Bilingualism \hfill Summer 2024
    \item PER 101: Intensive Elementary Persian \hfill Summer 2022
\end{itemize}

\subsection*{Stony Brook University - Teaching Assistant}
\begin{itemize}
    \item LIN 200: Language in the United States \hfill Spring 2026, Fall 2024
    \item LIN 345 Writing Systems of the World \hfill Fall 2025
    \begin{itemize}[label={$\circ$}]
        \item \textbf{Guest Lecturer}: Delivered two specialized sessions on "Middle Eastern Writing Systems," focusing on the evolution and structure of Persian and Kurdish orthographies.
    \end{itemize}
    \item LIN 431: The Structure of an Uncommonly Taught Language: \textbf{Behbahani} \hfill Spring 2024
    \begin{itemize}[label={$\circ$}]
        \item \textbf{Guest Lecturer \& Consultant}: Delivered the introductory lecture on the sociolinguistic background and typological features of Behbahani; provided ongoing linguistic consultancy for student fieldwork and data analysis.
    \end{itemize}
    \item LIN 320: Structure of English Language \hfill Fall 2023
    \item LIN 340: Historical Linguistics \hfill Spring 2023
    \item LIN 307: Sociolinguistics \hfill Fall 2022
    \item LIN 431: The Structure of an Uncommonly Taught Language: \textbf{Tati}  \hfill Spring 2022
    \item LIN 270: Language and Politics \hfill fall 2021
\end{itemize}

\subsection*{Additional Teaching Assistant}
\textbf{The NYI Global Institute of Cultural, Cognitive, and Linguistic Studies}
\begin{itemize}
    \item  Phonology Seminar: Strict CV Metrics or How to Live without Moras- \hfill Summer 2024
    \item Introduction to Syntax \hfill Winter 2024, Summer 2023 
    \item Introduction to Syllable Structure \hfill Winter 2024
    \item Experimental Linguistics \hfill Winter 2022
    \item Semantics Seminar: Missing words and missing worlds \hfill winter 2022
    \item Linguistics field method \hfill Summer 2021
    \item Semantics Seminar: Three or Four Puzzles about Numerals \hfill Summer 2021
\end{itemize}
\subsection*{Additional Instruction}
\begin{itemize}
    \item English Language and Literature Instructor. Tavana high school, Behbahan, Iran. \hfill 2012-2021
    
\end{itemize}
\section*{Professional Experience}
\begin{itemize}[leftmargin=0.5cm, label={}]
    % تجربه اول: NYI
    \item \textbf{Regional Outreach and Recruitment Coordinator for Iran} \hfill 2024 -- Present \\
    \textit{The NYI Global Institute of Cultural, Cognitive, and Linguistic Studies}
    \begin{itemize}[leftmargin=0.5cm, label={$\bullet$}]
        \item Lead student outreach and recruitment efforts in Iran, expanding access to international higher-education programs.
        \item Facilitate communication between prospective students and academic departments to streamline enrollment.
    \end{itemize}

    \vspace{0.15in}

    % تجربه دوم: SASC
    \item \textbf{Staff Member, Student Accessibility Support Center (SASC)} \hfill 2023 -- 2025 \\
    \textit{Stony Brook University}
    \begin{itemize}[leftmargin=0.5cm, label={$\bullet$}]
        \item Support students with accessibility needs through academic assistance and secure exam proctoring.
        \item Ensure compliance with accommodation regulations and maintain a distraction-free testing environment.
    \end{itemize}

    \vspace{0.15in}

    % تجربه سوم: Research Assistant
    \item \textbf{Graduate Research Assistant} \hfill Winter 2025 \\
    \textit{Stony Brook University}
    \begin{itemize}[leftmargin=0.5cm, label={$\bullet$}]
        \item \textbf{Collaborative Website Design for Tamil Research}: Developed a specialized website to showcase Tamil linguistic projects and facilitate global research collaboration.
        \item Integrated data resources to make the Tamil Research Group more accessible to the international linguistics community.
    \end{itemize}
\end{itemize}

\section*{Honors, Awards and Grants}
\begin{itemize}[leftmargin=0.5cm, label={$\bullet$}]
    \item \textbf{Research Fellowship}, Stony Brook University \hfill 2021
    \item \textbf{Travel Grant}, Department of Linguistics, Stony Brook University (for PLC 50) \hfill 2026
    \item \textbf{Travel Grant}, Department of Linguistics, Stony Brook University (for LSA) \hfill 2025
    \item \textbf{Travel Grant}, Department of Linguistics, Stony Brook University (for LSA) \hfill 2024
    \item \textbf{1st Place, Distinguished Student Award}, University of Kurdistan \hfill 2017
    \item \textbf{Ranked 35th (Top 1\%)}, National M.A. Linguistics Exam (~3,000 candidates) \hfill 2016
    
    \item \textbf{Best Student-Led Scientific Society Award}, University of Kurdistan \hfill 2014
\end{itemize}


\section*{Service \& Outreach}
\subsection*{Stony Brook University}
\cvsubsection{\textbf{Departmental/ University}}
\begin{itemize}[leftmargin=0.5cm, itemsep=0em, parsep=0.3em, topsep=0em]
    \item \textbf{President}, Stony Brook Linguistics Club \hfill 2022--2024
\end{itemize}
\vspace{1em}
\cvsubsection{\textbf{Professional Service}}
\begin{itemize}[leftmargin=0.5cm, itemsep=0em, parsep=0.3em, topsep=0em]
    \item \textbf{Reviewer}, Stony Brook–Yale–NYU–CUNY (SYNC) Conference \hfill 2021, 2025
\end{itemize}
\vspace{1em}
\cvsubsection{\textbf{Outreach}}
\begin{itemize}[leftmargin=0.5cm, itemsep=0em, parsep=0.3em, topsep=0em]
    \item \textbf{Instructor}, North American Computational Linguistics Open Competition (NACLO) \hfill 2026
\begin{itemize}[label={$\circ$}, leftmargin=0.4cm]
        \item Prepared high school students for linguistic challenges by introducing formal patterns, structural analysis, and computational logic.
    \end{itemize}\end{itemize}

\subsection*{University of Kurdistan}
\begin{itemize}[leftmargin=0.5cm, itemsep=0em, parsep=0.3em, topsep=0em]
    \item \textbf{Coordinator}, Departmental Colloquium on Linguistics and Cognitive Science \hfill 2012--2017
    \item \textbf{Coordinator}, Opening Ceremony of the Kurdish Studies Institute \hfill 2017
    \item \textbf{Executive Member}, Second National Conference on Reading \hfill 2017
    \item \textbf{Representative}, Linguistics Student Society \hfill 2016--2017
\end{itemize}

\section*{Languages}
\begin{itemize}[leftmargin=0.5cm]
    \item \textbf{Native:} Behbahani, Persian
    \item \textbf{Advanced:} English, Sorani Kurdish
    \item \textbf{Heritage:} Lori
    \item \textbf{Fieldwork:} Ardalani Kurdish, Kalhori Kurdish, Southern Tati
    \item \textbf{Beginner:} Turkish
\end{itemize}

\section*{Computing}
\begin{itemize}[itemsep=0.3em]
    \item \textbf{Programming:} 
      \begin{itemize}[label={--}, leftmargin=0.4cm]
            \item \textbf{Proficient:} \LaTeX, Git/GitHub
            \item \textbf{Working Knowledge:} Python, R, Haskell, HTML
        \end{itemize}
    \item \textbf{Experimental Tools:} Praat, ELAN, Qualtrics
\end{itemize}

\vspace{8pt}

\begin{center}
    Updated \today
\end{center}
\end{document}
